# Final Energy Demand


## Final Energy by carrier

### Total
```{r}
tot <- "FE|Transport edge"
items <- c(
  "FE|Transport edge|Electricity",
  "FE|Transport edge|Hydrogen",
  "FE|Transport edge|Gases",
  "FE|Transport edge|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Total w/o bunkers
```{r}
tot <- "FE|Transport edge|w/o bunkers"
items <- c(
  "FE|Transport edge|w/o bunkers|Electricity",
  "FE|Transport edge|w/o bunkers|Hydrogen",
  "FE|Transport edge|w/o bunkers|Gases",
  "FE|Transport edge|w/o bunkers|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Road
```{r}
tot <- "FE|Transport|Road"
items <- c(
  "FE|Transport|Road|Electricity",
  "FE|Transport|Road|Liquids",
  "FE|Transport|Road|Hydrogen",
  "FE|Transport|Road|Gases"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger
```{r}
tot <- "FE|Transport edge|Pass"
items <- c(
  "FE|Transport edge|Pass|Electricity",
  "FE|Transport edge|Pass|Hydrogen",
  "FE|Transport edge|Pass|Gases",
  "FE|Transport edge|Pass|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger w/o bunkers
```{r}
tot <- "FE|Transport|Pass|w/o bunkers"
items <- c(
  "FE|Transport|Pass|w/o bunkers|Electricity",
  "FE|Transport|Pass|w/o bunkers|Hydrogen",
  "FE|Transport|Pass|w/o bunkers|Gases",
  "FE|Transport|Pass|w/o bunkers|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger w/o bunkers
```{r}
tot <- "FE|Transport|Pass|w/o bunkers"
items <- c(
  "FE|Transport|Pass|w/o bunkers|Electricity",
  "FE|Transport|Pass|w/o bunkers|Hydrogen",
  "FE|Transport|Pass|w/o bunkers|Gases",
  "FE|Transport|Pass|w/o bunkers|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger LDV Four Wheelers
```{r}
tot <- "FE|Transport|Pass|Road|LDV|Four Wheelers"
items <- c(
  "FE|Transport|Pass|Road|LDV|Four Wheelers|Electricity",
  "FE|Transport|Pass|Road|LDV|Four Wheelers|Hydrogen",
  "FE|Transport|Pass|Road|LDV|Four Wheelers|Gases",
  "FE|Transport|Pass|Road|LDV|Four Wheelers|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger LDV Two Wheelers
```{r}
tot <- "FE|Transport|Pass|Road|LDV|Two Wheelers"
items <- c(
  "FE|Transport|Pass|Road|LDV|Two Wheelers|Electricity",
  "FE|Transport|Pass|Road|LDV|Two Wheelers|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger Bus
```{r}
tot <- "FE|Transport|Pass|Road|Bus"
items <- c(
  "FE|Transport|Pass|Road|Bus|Electricity",
  "FE|Transport|Pass|Road|Bus|Hydrogen",
  "FE|Transport|Pass|Road|Bus|Gases",
  "FE|Transport|Pass|Road|Bus|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger Rail (non-HSR)
```{r}
tot <- "FE|Transport|Pass|Rail|non-HSR"
items <- c(
  "FE|Transport|Pass|Rail|non-HSR|Electricity",
  "FE|Transport|Pass|Rail|non-HSR|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Passenger Aviation
```{r}
tot <- "FE|Transport|Pass|Aviation"
showLinePlots(data, tot)
```

### Freight
```{r}
tot <- "FE|Transport edge|Freight"
items <- c(
  "FE|Transport edge|Freight|Electricity",
  "FE|Transport edge|Freight|Hydrogen",
  "FE|Transport edge|Freight|Gases",
  "FE|Transport edge|Freight|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Freight w/o bunkers
```{r}
tot <- "FE|Transport|Freight|w/o bunkers"
items <- c(
  "FE|Transport|Freight|w/o bunkers|Electricity",
  "FE|Transport|Freight|w/o bunkers|Hydrogen",
  "FE|Transport|Freight|w/o bunkers|Gases",
  "FE|Transport|Freight|w/o bunkers|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Freight Trucks
```{r}
tot <- "FE|Transport|Freight|Road"
items <- c(
  "FE|Transport|Freight|Road|Electricity",
  "FE|Transport|Freight|Road|Hydrogen",
  "FE|Transport|Freight|Road|Gases",
  "FE|Transport|Freight|Road|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Freight Rail 
```{r}
tot <- "FE|Transport|Freight|Rail"
items <- c(
  "FE|Transport|Freight|Rail|Electricity",
  "FE|Transport|Freight|Rail|Liquids"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

### Freight Navigation
```{r}
tot <- "FE|Transport|Freight|Navigation"
showLinePlots(data, tot)
```

### Freight Shipping International
```{r}
tot <- "FE|Transport|Freight|International Shipping"
showLinePlots(data, tot)
```

## Final Energy Liquids by fuel shares (syn| bio| fossil)

### LDV
```{r}
tot <- "FE|Transport|Pass|Road|LDV|Liquids"

items <- c(
  "FE|Transport|Pass|Road|LDV|Liquids|Fossil",
  "FE|Transport|Pass|Road|LDV|Liquids|Hydrogen",
  "FE|Transport|Pass|Road|LDV|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### Bus
```{r}
tot <- "FE|Transport|Pass|Road|Bus|Liquids"

items <- c(
  "FE|Transport|Pass|Road|Bus|Liquids|Fossil",
  "FE|Transport|Pass|Road|Bus|Liquids|Hydrogen",
  "FE|Transport|Pass|Road|Bus|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### Rail
```{r}
tot <- "FE|Transport|Pass|Rail|Liquids"

items <- c(
  "FE|Transport|Pass|Rail|Liquids|Fossil",
  "FE|Transport|Pass|Rail|Liquids|Hydrogen",
  "FE|Transport|Pass|Rail|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### Aviation domestic
```{r}
tot <- "FE|Transport|Pass|Aviation|Domestic|Liquids"

items <- c(
  "FE|Transport|Pass|Aviation|Domestic|Liquids|Fossil",
  "FE|Transport|Pass|Aviation|Domestic|Liquids|Hydrogen",
  "FE|Transport|Pass|Aviation|Domestic|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### Aviation International
```{r}
tot <- "FE|Transport|Pass|Aviation|International|Liquids"

items <- c(
  "FE|Transport|Pass|Aviation|International|Liquids|Fossil",
  "FE|Transport|Pass|Aviation|International|Liquids|Hydrogen",
  "FE|Transport|Pass|Aviation|International|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### Trucks
```{r}
tot <- "FE|Transport|Freight|Road|Liquids"

items <- c(
  "FE|Transport|Freight|Road|Liquids|Fossil",
  "FE|Transport|Freight|Road|Liquids|Hydrogen",
  "FE|Transport|Freight|Road|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### Freight rail
```{r}
tot <- "FE|Transport|Freight|Rail|Liquids"

items <- c(
  "FE|Transport|Freight|Rail|Liquids|Fossil",
  "FE|Transport|Freight|Rail|Liquids|Hydrogen",
  "FE|Transport|Freight|Rail|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### Navigation
```{r}
tot <- "FE|Transport|Freight|Navigation|Liquids"

items <- c(
  "FE|Transport|Freight|Navigation|Liquids|Fossil",
  "FE|Transport|Freight|Navigation|Liquids|Hydrogen",
  "FE|Transport|Freight|Navigation|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

### International Shipping
```{r}
tot <- "FE|Transport|Freight|International Shipping|Liquids"

items <- c(
  "FE|Transport|Freight|International Shipping|Liquids|Fossil",
  "FE|Transport|Freight|International Shipping|Liquids|Hydrogen",
  "FE|Transport|Freight|International Shipping|Liquids|Biomass"
)
showAreaAndBarPlots(data, items, tot, orderVars = "user")
walk(items, showLinePlots, data = data)
```

## Final Energy by transport modes

### Passenger
```{r}
tot_wbunk <- "FE|Transport edge|Pass"
tot_wobunk <- "FE|Transport|Pass|w/o bunkers"
items <- c(
  "FE|Transport|Pass|Aviation|International",
  "FE|Transport|Pass|Aviation|Domestic",
  "FE|Transport|Pass|Rail|HSR",
  "FE|Transport|Pass|Rail|non-HSR",
  "FE|Transport|Pass|Road|Bus",
  "FE|Transport|Pass|Road|LDV|Four Wheelers",
  "FE|Transport|Pass|Road|LDV|Two Wheelers"
)
showAreaAndBarPlots(data, items, tot_wbunk, orderVars = "user")
showAreaAndBarPlots(data, items[2:7], tot_wobunk, orderVars = "user")
showAreaAndBarPlots(data, items, tot_wbunk, fill = TRUE, orderVars = "user")
showAreaAndBarPlots(data, items[2:7], tot_wobunk, fill = TRUE, orderVars = "user")
showLinePlots(data, tot_wbunk)
walk(c("FE|Transport|Pass|Aviation", items[1:5], "FE|Transport|Pass|Road|LDV", items[6:7]), showLinePlots, data = data)
```

### Freight
```{r}
tot_wbunk <- "FE|Transport|Freight edge"
tot_wobunk <- "FE|Transport|Freight|w/o bunkers"
items <- c(
  "FE|Transport|Freight|International Shipping",
  "FE|Transport|Freight|Navigation",
  "FE|Transport|Freight|Rail",
  "FE|Transport|Freight|Road"
)
showAreaAndBarPlots(data, items, tot_wbunk, orderVars = "user")
showAreaAndBarPlots(data, items[2:4], tot_wobunk, orderVars = "user")
showAreaAndBarPlots(data, items, tot_wbunk, fill = TRUE, orderVars = "user")
showAreaAndBarPlots(data, items[2:4], tot_wobunk, fill = TRUE, orderVars = "user")
walk(items, showLinePlots, data = data)
```
